\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}

\begin{document}

\section*{Design Specification – SportHub}

\section{Overview}
SportHub is a web application that lets users view upcoming games for
multiple sports and keep a personal list of favorite games. This document
describes the planned screens and main UI elements.

\section{Global Layout}
All pages share:
\begin{itemize}
  \item A top navigation bar with links:
        \textbf{SportHub}, \textbf{All Games}, \textbf{My Favorites},
        and (later) \textbf{Admin}.
  \item A consistent color theme and typography.
  \item A footer with basic information about the team or course.
\end{itemize}

\section{All Games Page}
\subsection*{Purpose}
Show all upcoming games so the user can quickly see what is happening
across different sports.

\subsection*{Main Elements}
\begin{itemize}
  \item \textbf{Filters area} at the top:
        \begin{itemize}
          \item Dropdown to select a sport (e.g., NBA, NFL, MLB).
          \item Date picker or simple date filter (e.g., Today, This Week).
        \end{itemize}
  \item \textbf{Games list} in the middle of the page:
        \begin{itemize}
          \item Each row/card shows sport, teams, date, time, and status.
          \item A favorite icon/button that the user can click to add or
                remove the game from favorites.
        \end{itemize}
\end{itemize}

\section{My Favorites Page}
\subsection*{Purpose}
Allow the user to focus only on games they care about most.

\subsection*{Main Elements}
\begin{itemize}
  \item Page title: \textbf{My Favorites}.
  \item Short description explaining that only favorited games appear here.
  \item List of favorite games with the same layout as the All Games page.
  \item Ability to unfavorite a game, which removes it from this list.
\end{itemize}

\section{Admin Page (Planned for Later Snapshot)}
\subsection*{Purpose}
Give project members a way to manage the list of games without directly
editing the database.

\subsection*{Main Elements}
\begin{itemize}
  \item Table showing existing games with Edit and Delete actions.
  \item Form for adding or editing a game with fields:
        sport, home team, away team, date, time, and optional status.
  \item Save / Cancel buttons for the form.
\end{itemize}

\end{document}
